Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-26 paper/paper.tex
Fix broken references

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.4\textwidth]{stretching_cybershake}
    \caption[Percentage of high scores achieved by each algorithm for Cybershake pareto unsorted ensembles when task runtime is stretched]{Percentage of high scores achieved by each algorithm for Cybershake pareto unsorted ensembles when task runtime is stretched. A stretching factor of $x$ means that the runtime of tasks in each workflow was multiplied by $x$.}
    \label{fig:stretching}
\end{figure}

@@

Figure~\ref{fig:variances}.b shows the ratio of actual makespan to budget. The interesting thing to notice about this figure is that, for all three algorithms, the deadline constraint is rarely exceeded, even in cases with very poor quality estimates. For the dynamic algorithms this is a result of the fact that they can adapt at runtime to changing circumstances to avoid exceeding the deadline. For the static algorithm this is a result of the way that SPSS schedules workflows and not of a particularly clever optimization. The SPSS algorithm tends to schedule workflows early, using up the budget long before the deadline is reached. This is a consequence of the deadline distribution function in SPSS, which prevents workflows from starting late. This is shown by the gantt chart in Figure~\ref{fig:spss-example}, which illustrates how SPSS tends to pile up workflows at the beginning of the timeline. In comparison, the dynamic algorithms tend to spread out workflow starts over the entire duration as shown in Figure~\ref{fig:spds-example}. The consequence of this behavior is that SPSS plans tend to use up the budget but leave plenty of time before the deadline. So when the runtime of the plan is increased by introducing errors, the SPSS plan has some room to expand without exceeding the deadline.

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-variations-test-0-output-cost-all}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
    \hspace{2cm}
        \includegraphics[width=0.4\textwidth]{run-finish-variations-test-0-output-makespan-all} }
    \caption[Boxplots for budget and deadline ratios when runtime estimates are inaccurate]{Boxplots for budget and deadline ratios when runtime estimate error varies from $\pm$0\% to $\pm$50\% for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:variances}
\end{figure*}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-delays-test-0-output-cost-montage}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \hspace{2cm}
        \includegraphics[width=0.4\textwidth]{run-finish-delays-test-0-output-dagfinish-montage}
        }
    \caption[Boxplots for budget and deadline ratios when provisioning delays occur]{Boxplots for budget and deadline ratios when provisioning delay varies from 0 seconds to 15 minutes for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:delays}
\end{figure*}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-failures-test-0-output-cost-all}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \hspace{2cm}
        \includegraphics[width=0.4\textwidth]{run-finish-failures-test-0-output-makespan-all}
        }
    \caption{Boxplots for budget and deadline ratios when failure rate varies
    from 0 seconds to 50 \% for all three algorithms. A value of 1
    indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:failures}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.4\textwidth]{spss_planning_time}
    \caption{Planning time of SPSS algorithm for ensembles of 100 workflows and different workflow sizes.}
    \label{fig:spss_planning_time}
\end{figure}

@@

% This balances the columns by inserting a column break at the given reference
\IEEEtriggeratref{13}

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics[width=0.3\textwidth]{stretching_cybershake}
    \caption[Percentage of high scores achieved by each algorithm for Cybershake pareto unsorted ensembles when task runtime is stretched]{Percentage of high scores achieved by each algorithm for Cybershake pareto unsorted ensembles when task runtime is stretched. A stretching factor of $x$ means that the runtime of tasks in each workflow was multiplied by $x$.}
    \label{fig:stretching}
\end{figure}

@@

Figure~\ref{fig:variances}.b shows the ratio of actual makespan to budget. The interesting thing to notice about this figure is that, for all three algorithms, the deadline constraint is rarely exceeded, even in cases with very poor quality estimates. For the dynamic algorithms this is a result of the fact that they can adapt at runtime to changing circumstances to avoid exceeding the deadline. For the static algorithm this is a result of the way that SPSS schedules workflows and not of a particularly clever optimization. The SPSS algorithm tends to schedule workflows early, using up the budget long before the deadline is reached. This is a consequence of the deadline distribution function in SPSS, which prevents workflows from starting late. This is shown by the gantt chart in Figure~\ref{fig:algorithm-example}b, which illustrates how SPSS tends to pile up workflows at the beginning of the timeline. In comparison, the dynamic algorithms tend to spread out workflow starts over the entire duration as shown in Figure~\ref{fig:algorithm-example}a. The consequence of this behavior is that SPSS plans tend to use up the budget but leave plenty of time before the deadline. So when the runtime of the plan is increased by introducing errors, the SPSS plan has some room to expand without exceeding the deadline.

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-variations-test-0-output-cost-all}
    }
    \hspace{2cm}
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=0.4\textwidth]{run-finish-variations-test-0-output-makespan-all}
    }
    \caption[Boxplots for budget and deadline ratios when runtime estimates are inaccurate]{Boxplots for budget and deadline ratios when runtime estimate error varies from $\pm$0\% to $\pm$50\% for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:variances}
\end{figure*}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-delays-test-0-output-cost-montage}
    }
    \hspace{2cm}
    \subfloat[Ratio of Actual Makespan to Deadline]{    
        \includegraphics[width=0.4\textwidth]{run-finish-delays-test-0-output-dagfinish-montage}
    }
    \caption[Boxplots for budget and deadline ratios when provisioning delays occur]{Boxplots for budget and deadline ratios when provisioning delay varies from 0 seconds to 15 minutes for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:delays}
\end{figure*}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-failures-test-0-output-cost-all}
    }
    \hspace{2cm}
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=0.4\textwidth]{run-finish-failures-test-0-output-makespan-all}
    }
    \caption{Boxplots for budget and deadline ratios when failure rate varies
    from 0 seconds to 50 \% for all three algorithms. A value of 1
    indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:failures}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.3\textwidth]{spss_planning_time}
    \caption{Planning time of SPSS algorithm for ensembles of 100 workflows and different workflow sizes.}
    \label{fig:spss_planning_time}
\end{figure}

@@

% This balances the columns by inserting a column break at the given reference
\IEEEtriggeratref{23}
